### 2017-12-23 example-short-chapter.tex
inventary

\begin{table}	
	\begin{center}
		\begin{tabular}{lcc}
			\toprule
			\textbf{Fiscal year}&\textbf{2015}&\textbf{2016}\\
			\midrule
			Income tax benefits/(expenses)&14,262&(179,500)\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Income tax benefits or expenses (in thousands of RMB \textyen)}\label{table:1}
\end{table}

@@

@@

\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lrr}
			\toprule
			\textbf{Fiscal year}&\textbf{2015}&\textbf{2016}\\
			\midrule
			Short-term borrowings&17,863,868&19,771,695\\
			Nonrecourse securitization debt&2,114,913&4,391,955\\
			Accounts payable&2,780,482&4,391,955\\
			Advance from customers&-&723,449\\
			Deferred revenues&8,193,665&17,464,408\\
			Taxes payable&927,177&1,423,736\\
			Amount due to related parties&20,539,543&28,909,438\\
			Accrued expenses and other current liabilities&3,698,488&12,697,915\\
			Total current liabilities&-&10,766,920\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Current liabilities (In thousands of RMB \textyen)}\label{table:1}
\end{table}

\chapter{Inventories}

>>>>

\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lcc}
			\toprule
			\textbf{Fiscal year}&\textbf{2015}&\textbf{2016}\\
			\midrule
			Current income tax expenses&(28,322)&(214,282)\\
			Deferred tax benefits&42,584&34,782\\
			\qquad\emph{Income tax benefits/(expenses)}&14,262&(179,500)\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Income tax benefits or expenses (in thousands of RMB \textyen)}\label{table:1}
\end{table}

@@

\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lrr}
			\toprule
			\textbf{Fiscal year}&\textbf{2015}&\textbf{2016}\\
			\midrule
			Cash and cash equivalents&17,863,868&19,771,695\\
			Restricted cash&2,114,913&4,391,955\\
			Short-term investments&2,780,482&4,391,955\\
			Investment securities&-&723,449\\
			Accounts receivable, net&8,193,665&17,464,408\\
			Advance to suppliers&927,177&1,423,736\\
			Inventories, net&20,539,543&28,909,438\\
			Loan receivables, net&3,698,488&12,697,915\\
			Other investments&-&10,766,920\\
			Prepayments and other current assets&1,486,441&2,198,906\\
			Amount due from related parties&863,516&1,410,050\\
			\qquad\emph{Total current assets}&58,468,093&106,932,098\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Current assets (in thousands of RMB \textyen)}\label{table:1}
\end{table}

@@

\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lrr}
			\toprule
			\textbf{Fiscal year}&\textbf{2015}&\textbf{2016}\\
			\midrule
			Short-term borrowings&3,040,209&8,333,317\\
			Nonrecourse securitization debt&579,843&9,389,213\\
			Accounts payable&29,819,341&4,391,955\\
			Advance from customers&7,173,885&43,988,087\\
			Deferred revenues&983,721&11,632,766\\
			Taxes payable&103,211&1,221,865\\
			Amount due to related parties&104,726&575,848\\
			Accrued expenses and other current liabilities&7,178,065&167,655\\
			\qquad\emph{Total current liabilities}&48,983,001&104,740,235\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Current liabilities (In thousands of RMB \textyen)}\label{table:1}
\end{table}

It indicates that the current liabilities jumped from \textyen104,726,000 to \textyen104,740,235,000.

\section{Working Capital}
\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lrr}
			\toprule
			\textbf{Fiscal year}&\textbf{2015}&\textbf{2016}\\
			\midrule
			Working capital&9,485,092&2,191,863\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Working capital (In thousands of RMB \textyen)}\label{table:1}
\end{table}

\section{Current Ratio}
\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lrr}
			\toprule
			\textbf{Fiscal year}&\textbf{2015}&\textbf{2016}\\
			\midrule
			Current ratio&1.194&1.021\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Current ratio}\label{table:1}
\end{table}

\section{Quick Ratio}
\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lrr}
			\toprule
			\textbf{Fiscal year}&\textbf{2015}&\textbf{2016}\\
			\midrule
			Quick ratio&29,819,341&4,391,955\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Quick ratio}\label{table:1}
\end{table}

\chapter{Inventories}
\section{Inventory Values}

Inventories, net, consist of the following\footnote{JD.com, Inc. annual report 2016, Page F-48}:
\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lrr}
			\toprule
			\textbf{Fiscal year}&\textbf{2015}&\textbf{2016}\\
			\midrule
			Products&20,436,275&28,778,528\\
			Packing materials and others&103,268&130,910\\
			\qquad\emph{Inventories, net}&20,539,543&28,909,438\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Inventories, net (in thousands of RMB \textyen)}\label{table:1}
\end{table}

\section{Inventory Valuation Policy}
Inventories, consisting of products available for sale, are stated at the lower of cost or market value\footnote{JD.com, Inc. annual report 2016, Page F-20}. Cost of inventory is determined using the weighted
average cost method. Adjustments are recorded to write down the cost of inventory to the estimated market value due to slow-moving merchandise and
damaged goods, which is dependent upon factors such as historical and forecasted consumer demand, and promotional environment. The Group takes
ownership, risks and rewards of the products purchased, but has arrangements to return unsold goods with certain vendors. Write downs are recorded in cost of
revenues in the Consolidated Statements of Operations and Comprehensive Loss.

The Group also provides fulfillment-related services in connection with the Group’s online marketplace. Third-party sellers maintain ownership of their
inventories and therefore these products are not included in the Group’s inventories.
\section{Gross Profit Percentage on Sale}

Based on the data of JD.com, Inc. consolidated statements of operations and comprehensive loss\footnote{JD.com, Inc. annual report 2016, Page F-48}, gross profit percentage on sale can be calculated as follows:

\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lrr}
			\toprule
			\textbf{Fiscal year}&\textbf{2015}&\textbf{2016}\\
			\midrule
			Revenue&181,275,425&260,121,645\\
			Cost of goods sold&157,008,329&220,698,727\\
			Gross profit&24,267,096&39,422,918\\
			Gross profit percentage&13.39\%&15.16\%\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Gross profit percentage on sale (in thousands of RMB \textyen\ except for gross profit percentage)}\label{table:1}
\end{table}

\section{Inventory Turnover}
Based on the data of JD.com, Inc. consolidated balance sheet\footnote{JD.com, Inc. annual report 2016, Page F-3 and JD.com, Inc. annual report 2015, Page F-3} and consolidated statements of operations and comprehensive loss\footnote{JD.com, Inc. annual report 2016, Page F-48}, gross profit percentage on sale can be calculated as follows:

\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lrr}
			\toprule
			\textbf{Fiscal year}&\textbf{2015}&\textbf{2016}\\
			\midrule
			Beginning inventory &12,190,843&20,539,543\\
			Ending inventory  &20,539,543&28,909,438\\
			Average inventory &16,365,193&24,724,490.5\\
			Cost of goods sold &157,008,329&220,698,727\\
			Inventory turnover &9.594&8.826\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Inventory turnover (in thousands of RMB \textyen\ except for inventory turnover)}\label{table:1}
\end{table}
